\documentclass{homework}
% \author{Prof. Tashfeen}
% \class{}
\title{Homework 0}
\address{Oklahoma City Community College}

\begin{document} \maketitle


Read and answer the questions bellow. I have answered them for myself,
you need to do the same but for yourself. Be as descriptive as you
like but don’t write me a book.

\question Tell us a little bit about yourself. What is your name,
hobbies, favourite food, natural languages you speak (wish you spoke),
add a picture if you like. This is information I can use to remember
you.

\begin{sol}
I am Tashfeen, I like to read, run, cook, program and watch TV. As for
food, I like anything spicy, tacos?  But, also the simple things like
brioche with butter. I speak English, Urdu and am learning French:
\textit{J’apprends le français mais je ne suis pas bon.}
\img<romeo>[0.3]{Tashfeen and their cat Romeo.}{tashfeen}
\end{sol}


\question What is your major? Why did you pick this major? If it is
computer science, what does computer science mean to you?

\begin{sol}
I was dual degree in mathematics and computer science. I got into
computers because of video games and a friend talked me into
maths. I’ll let you define computer science.
\end{sol}

\question How would you categorise yourself in college \eg freshman,
sophomore etc.

\begin{sol}
Well, I am a PhD student at OU.
\end{sol}

\question What are your career goals and why are you in school?

\begin{sol}
People tell me I am good at it, I tend to agree.
\end{sol}

\question Have you ever had me in some other course? If yes, which one?

\begin{sol}
Well, yes of course, I have always had Tashfeen in all of my courses.
\end{sol}

\question Do you have any programming experience? Which languages?

\begin{sol}
I have written code in almost all of them...
\end{sol}

\question How good/bad are you with computing-technology?

\begin{sol}
You are not a good computer scientist if you are not bad with technology.
\end{sol}

\question Why are you in this course?

\begin{sol}
I am teaching it.
\end{sol}

\question What is the best way you learn?

\begin{sol}
By making mistakes.
\end{sol}

\question Is there anything I should know about you \textit{as your
  professor}?

\begin{sol}
Yes, I am you.
\end{sol}

\question Solve the following two (not a system of) equations for the
value of $x$,
\[
    (x-47)^2=0
\]
and,
\[
    x^2-46=3
\]

\begin{sol}
Complete the square if you want to impress me. Fun fact, the ancient
Egyptians knew a similar method.
\end{sol}

\question Have you read the syllabus (at online classroom) and and
plan to abide by it?

\begin{sol}
Yes.
\end{sol}

\end{document}
